---
title: "Lab01_RZhong"
author: "Rongkai Zhong"
date: "2023-10-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Visualizations
```{r}
boulder <- st_read("C:/Users/rongkaiz/Downloads/rzhong/BoulderSocialMedia.shp")
boulder
summary(boulder)
```

### Plots

Compare the distance from trails and social media photographs
```{r}
boulder %>%
  filter(DB ==  'Pano' | DB == 'Flickr') %>%
  ggplot(aes(x=DB, y=Trails_dis)) + 
  geom_boxplot()
```
### Graduated color maps

Use graudated colors to visualize the distances to the trails.
```{r}
ggplot() +
    geom_sf(data =boulder, aes(color=Trails_dis),
    fill = NA, alpha = .2) +
    scale_colour_gradientn(colours = inferno(10))
```

```{r}
library(tmap)
```

Use trail distances to depict the pattern of trails of Boulder.
```{r}
## Add the data - these are specific to the vector or raster
tm_shape(boulder) + 
  ## which variable, is there a class interval, palette, and other options
  tm_symbols(col='Trails_dis', 
             style='quantile', 
             palette = 'Greys',
             border.lwd = NA,
             size = 0.1)
```
## Questions

Discuss the advantages and challenges associated with an open data science approach. Provide an example based on this week’s reading. (1-2 paragraphs)

Create a markdown document that showcases an analysis of this week’s data or any other dataset of your choice. Include descriptive text that explains your analysis, and incorporate figures and geovisualizations.Include 1 chart and 1 map. Structure and explain your analysis with text, headings, highlights, images and other markdown basics.